Hadoop Image Processing Framework

### 2015-03-15 Paper.tex
Updated charts and observations section

\begin{figure}[h]
	\centering
	\includegraphics[width=0.45\textwidth]{module-chart}
	\caption{Module Chart}
	\label{fig:module-chart}
\end{figure}

@@

@@

The great thing about Hadoop Image Processing framework is its built in such a way that using it is really simple. The framework strictly adheres java file writing and reading techniques and extends it to a new level of BundleFile Writing and Reading using hadoop framework. This makes user to work with hadoop image processing more flexible and easier. The main aim of the framework is to provide an abstractness in such a way that programming on a single computer is equivalent to programming on a hadoop cluster.  Listing 1. provides the similarities in code writing in java and image processing framework. Making framework similar to java helps understanding the framework more easier and reduces complexity.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.45\textwidth]{files-chart}
	\caption{Comparing File Writers and readers without and with using framework }
	\label{fig:files-chart}
\end{figure}

@@

\section{Conclusion}
This paper has described our framework fo image processing for large scale image processing applications on the MapReduce framework. The framework is designed to abstract the technical details of Hadoop's powerful MapReduce framework and provide a way for users who want to process large image datasets. We provided a how the images can be stored in different hadoop file format and efficient access within Map Reduce pipeline and simple modules to make the framework more easier. By providing interoperability between different image data types we give the user to process the images using different open-source image processing libraries. Finally, we provide a way to overcome the loss of image headers after processing which are most useful for image processing and vision applications.

>>>>

@@

We have documented the following samples in the space of image processing
computations, and hardware and software configurations applied to the selected
data set.
\begin{itemize}
	\item Three image processing computations described in Table 1.
	\item Sampled data set of different image counts.
	\item Hardware cluster configurations used for computations. 
	\item Coding complexities in different environments for the three image processing computations
\end{itemize}

The numerical results are shown in Figure 1 through 6.

Figure \ref{fig:perf-chart} illustrates the performance comparison of Single Node, Hadoop using framework and Hadoop without using the framework for Canny Edge Detection.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.45\textwidth]{perf-graph}
	\caption{Canny Edge Detection computations executed on single node and on a Hadoop cluster with and without using framework}
	\label{fig:perf-chart}
\end{figure}
It can be observed that the performance hadoop cluster is almost the same with and without using framework. The framework performs well sometimes because of multi-threading is implemented few tasks. Considering the single node performance it can be seen that the single node outperforms hadoop if the input is small as the input size increases handling huge data becomes infeasible. The same pattern is observed with any image processing algorithm.

Figure \ref{fig:module-chart} compares coding complexities of different modules the framework described. The Downloader module and Extractor module are simple to use and require less number of lines of code to configure. The processor module includes the algorithm the user devised, which adds up a few extra lines of code. but configuring the devised algorithm to a MapReduce job is fairly simple with very less number of steps. The modules are included with different methods for flexibility.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.45\textwidth]{module-chart2}
	\caption{Comparing coding complexities of modules in different environments}
	\label{fig:module-chart}
\end{figure}

Figure \ref{fig:comp-chart} shows the coding complexities of three image processing computations from Table 1. Single node and the framework show similar coding complexity outperforming the image processing without framework. The reason behind this is Hadoop Image Processing Framework hides the inner details of MapReduce programming which makes an user to think that he is working on the single node but actually the task is processed in hadoop. Without the framework user needs to write a MapReduce job which is cumbersome.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.45\textwidth]{comp-chart}
	\caption{Comparing coding complexities of laplacian filter, canny edge detection and k-means clustering  in different environments}
	\label{fig:comp-chart}
\end{figure}

@@

The great thing about Hadoop Image Processing framework is its built in such a way that using it is really simple. The framework strictly adheres java file writing and reading techniques and extends it to a new level of BundleFile Writing and Reading using hadoop framework. This makes user to work with hadoop image processing more flexible and easier. The main aim of the framework is to provide an abstractness in such a way that programming on a single computer is equivalent to programming on a hadoop cluster.  Listing 1. provides the similarities in code writing in java and image processing framework. Making framework similar to java helps understanding the framework more easier and reduces complexity. Listing 2 shows a sample code for setting image headers for processed images.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.45\textwidth]{files-chart2}
	\caption{Comparing File Writers and readers without and with using framework }
	\label{fig:files-chart}
\end{figure}

@@

\begin{lstlisting}[caption = Setting image headers for processed images using Hadoop Image Processing Framework]

//input - HImage is sent as input

CannyEdge canny = new CannyEdge(input);
canny.process();
HImage himage = canny.getProcessedImage();
himage.setImageHeader(input.getImageHeader());

\end{lstlisting}
\section{Conclusion}
This paper has described our framework fo image processing for large scale image processing applications on the MapReduce framework. The framework is designed to abstract the technical details of Hadoop's powerful MapReduce framework and provide a way for users who want to process large image datasets. We provided a how the images can be stored in different hadoop file format and efficient access within Map Reduce pipeline and simple modules to make the framework more easier. By providing interoperability between different image data types we give the user to process the images using different open-source image processing libraries. Finally, we provide a way to overcome the loss of image headers after processing which are most useful for image processing and vision applications.
